\begin{piosenka_dluga}[1mm]{Do I wanna know -- Arctic Monkeys}

Have you got colour in your cheeks? & fis D h \\*
Do you ever get the fear that you can't shift the type & h fis \\*
That sticks around like summat in your teeth? & fis \\*
Are there some aces up your sleeve? & D h \\*
Have you no idea that you're in deep? & fis \\*
I dreamt about you nearly every night this week & fis \\*
How many secrets can you keep? & D h \\*
Cause there's this tune I found that makes me \\*
\hspace{20mm} think of you somehow & fis \\*
And I play it on repeat & fis \\*
Until I fall asleep & D h \\*
Spilling drinks on my settee & Cis \\[\zwrotkaspace]

\refrenspace Do I wanna know & D \\*
\refrenspace If this feeling flows both ways? & h \\*
\refrenspace Sad to see you go & fis \\*
\refrenspace Was sorta hoping that you'd stay & fis \\*
\refrenspace Baby we both know & D \\*
\refrenspace That the nights were mainly made & h \\*
\refrenspace For saying things that you can't say tomorrow day & fis \\[\zwrotkaspace]

\refrenspace Crawlin' back to you & fis \\*
\refrenspace Ever thought of calling when you've had a few & D h \\*
\refrenspace Cos I always do & fis \\*
\refrenspace Maybe I'm too busy being yours to fall for somebody new & fis D h \\*
\refrenspace Now I've thought it through & fis \\*
\refrenspace Crawlin' back to you & fis \\[\zwrotkaspace]

So have you got the guts? & fis D h \\*
Been wondering if your heart's still open & h h fis \\*
And if so I wanna know what time it shuts & fis \\*
Simmer down and pucker up & D h \\*
I'm sorry to interrupt & fis \\*
It's just I'm constantly on the cusp & fis \\*
Of trying to kiss you & D h \\*
I don't know if you feel the same as I do & fis \\*
But we could be together & D h \\*
I you wanted to & Cis \\[\zwrotkaspace]

\refrenspace Do I wanna know\ldots \\[\zwrotkaspace]
\refrenspace Crowling back to you\ldots \\[\zwrotkaspace]
\refrenspace Do I wanna know\ldots \\[\zwrotkaspace]

Do I wanna know & D \\*
Too busy being yours to fall & h \\*
Sad to see you go & Fis \\*
Ever thought of calling darling? & E \\*
Do I wanna know & D \\*
Do you want me crawling back to you? & h fis \\*

\end{piosenka_dluga}